Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Initial conclusion

\begin{itemize}
	\item Conclude the work done in the paper
	\item Hint to some future work developments
\end{itemize}

>>>>

To choose an appropriate planner for the domain involving Unmanned Aerial
Vehicles, we have given an overview of probabilistic planning. Probabilistic
planning problems are usually represented in Markov Decision Processes. The
IPPC, a competition for probabilistic planners, used Goal-Oriented MDPs for
benchmark domains.

Little et al\. however argued for \emph{probabilistic
interestingness}. Little et al\. proposed a test to test for \emph{probabilistic
interestingness}: a) multiple goal trajectories, b) at least one pair of goal
trajectories that have a common initial sequence and c) there is at least one
goal trajectory that if a action is executed the probability reaching a dead
end decreases.

Two types of probabilistic planners are MDP solvers and replanners.
Surprisingly replanners performed extremely well in the first IPPC
competitions, especially FF-Replan in IPPC-04. Later, with FH-MDPs replanners
failed to be scalable and sensitive to an expected reward maximization, the
evaluation criteria for those domains. \textsc{Gourmand} is a state-of-the-art
MDP solver that performed better than other planners like \textsc{Glutton} or
PROST.

To choose an appropriate planner for the UAV domain, we have discussed other
existing benchmark domains used in the IPPC.
